The paper on \Large \bf Blockchain Frontrunning

### 2018-09-17 frontrunning/Latex/sections/paper.tex
[frontrunning] finish one round edits + more citations

In the traditional markets, front-running is considered unethical and also illegal. In the blockchain space, the designers of the decentral applications cannot rely on the justice system for unethical behavior, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain order books. The methods discussed within these projects prevent blockchain network participants from front running the orders as the orders are private and not known to the network and will not be broadcasted. However they are introducing third parties, \eg relayers in 0xproject, to be managing the orders with the promise not to reorder or front-run other orders.

\emph{Traditional Front-running Prevention Methods}. There are debates in traditional markets regarding the fact that Front-running is considered to be a form of insider trading which deemed to be illegal. Traditional methods to prevent front-running mainly involves after the fact investigation and legal action against the front-runners~\cite{LexisNexisLawSuit}. As mentioned in section~\ref{traditionalFrontrunning}, educating the employees were the first step taken to prevent such issues in traditional markets, however front-running became less likely to happen mainly because of the high fine and law suits against firms whom behaved in an unethical way. Other methods such as dark pools~\cite{zhu2014dark, buti2011diving} and sealed bids~\cite{radner1989sealed} were discussed and implemented in variety of regulated trading systems.

@@

There are two main approaches to prevent front running, one to design a blockchain that is front-run resistant , and the other to design the application logics in a way that front running is not possible. 
%______________________________________________________________%
\subsection{Front-run Resistant Blockchain}
What does this mean to have a front-run resistant blockchain?  There are technical difficulties to achieve such solutions as there are unknown factors within such network designs (corner/edge cases). In this section, we describe the potential solutions using which, one can design and implement a decentral application that is resistant to front-running.

\subsubsection{Design Decision \#1: Fixed Transaction Ordering\newline}

One possible solution to fix current blockchains in regards to transaction reordering by miners has been proposed by da Silva~\etal~\cite{fixedordering2018silva}. This solution consists of an algorithm, known as Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions.

\subsubsection{Design Decision \#2:Privacy Preserving Blockchain\newline}

Market participants are concerned about revealing information on their past trades, purchases, income, or liquidity needs. Privacy is a basic human right, that being said, there are limitations with the functionality of a system designed to preserve full privacy. However other than past transactions, real time transactions could leak informations about the sender or the intention of the order that could lead to front-running attacks. Privacy preserving blockchains try to solve the initial issue by keeping all the details of the transactions private, in some extent~\cite{miller2017empirical, kappos2018empirical}. 
As an example, ZCash~\cite{hopwood2016zcash}, uses two distinct type of addresses, transparent addresses and shielded addresses. Transparent addresses work similar to Bitcoin transactions, fully transparent about the sender and receiver addresses, the amount and included data. However shielded addresses are private and do not leak any information, this is great for privacy but not good for smart contracts capabilities. Smart contract functionality requires verification by the miners which require to know the input, functionality and output of smart contracts to be able to determine if the transaction is valid. Albeit by using cryptographic primitives such as zero-knowledge proofs this issue could also be resolved~\cite{kosba2016hawk}.

\subsubsection{Design Decision \#3: Dual Authoring\newline}

Loopring is an open protocol proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}. This protocol operates a hybrid model with off-chain order management and communication and merely the order matching takes place on the chain. To achieve high liquidity and price improvement, Loopring orders are grouped in \emph{ring orders}. After the required signatures are provided by a miner and owner of the order, see Figure~\ref{fig:vulnerable_loopring}, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement. While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address and then sign the hash of the ring using his own private key. By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}. However, Loopring's team solves this issue using the \emph{dual-authoring} scheme in the new version of the Loopring protocol. This solution sets two levels of authorization for orders - one for settlement, and one for order matching. As it can be seen in Figure~\ref{fig:not_vulnerable_loopring}, each owner of any order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key. These auth-keys are used to sign the hash of the ring and will further prevent anyone from regenerating the same \emph{submitRing transaction}. The reason is that the auth-keys are only known to the miner of the ring as they are not part of on-chain transaction. Doing so, it is assured that (i) the orders are not modified (because they are signed using the owner's private key), (ii) no other miner can mine the ring (because the miner's address is signed using his private key), and no user can front-run the \emph{submitRing transaction} (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).

@@

Another method to prevent front-running activities is to design the applications, whether they are decentralized (Dapps) or centralized, in such a way that no information would be available to the malicious parties to enable them to front-run the other users.
Followings discuss the two techniques which can be used by the Apps/DApps developers while designing the systems to prevent front-running activities.

\subsubsection{Design Decision \#1: Commitment Scheme\newline} \label{CommitmentScheme} %talk about the drawbacks of this scheme: eg: you may forget to reveal. 
Commitment scheme is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}. Commitment scheme is a robust method to prevent information leakage from the sensitive transactions. This could be done by simply broadcasting the hash value of the committed data and later on revealing the values that would be hashed to the committed hash, see Figure~\ref{fig:commitReveal}. 
In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order. Depending on the Dapp design, either the order is collateralized, which means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be considered as a DoS attack. 
Another use of such commitment scheme, is in decentralized naming systems, such as Namecoin, Ethereum Name Service (ENS) or Ghazal. In this case, a user sends a commit transaction, which commits to the name hash, similar to a sealed bid. Once the transaction is confirmed and the grace period is over, user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}. Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running. Similar approach applies to on-chain voting as well ~\cite{adChainPLCRVoting}, using sealed votes, voters can make sure their votes are hidden until a later date, however their participation and weight of the vote are publicly known. 
Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor. For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, It will be obvious that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme. Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design. On the other note, these method has some drawbacks, the user experience is not smooth and one might forget to reveal the committed transaction. In ENS commit-reveal process, if one forgets to reveal on the reveal phase, the committed funds are burnt and inaccessible there after. Also this scheme means two transaction are required for a functionality which is makes it more expensive to run.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\linewidth]{figures/commit-reveal.png}
\caption{ Commit and Reveal. User sends a commitment transaction with the hash of the data, After the commitment period is over, user sends her reveal transaction to the DApp revealing the information that matches the commitment. \label{fig:commitReveal}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3cd4c865-83d4-4c71-9a4a-f2e870f2db2c

\subsubsection{Design Decision \#2: Submarine Commitments\newline}\label{submarineCommits}
Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} are similar to the commitment schemes with some key differences such as hiding participatory factor and being fully collateralized. However, they could be design in other ways to suit the need of the DApp. With submarine send, it is possible to hide sender, receiver, value and data, the commitment transaction is identical to a transaction to a newly generated address. Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants.

The details of how Submarine commitments work is outside the scope of this paper, however in summary, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address in which no private key exists. By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}.  Drawbacks of this scheme are similar to ~\ref{CommitmentScheme}, with an addition of two more transactions to finalize the functionality, which results in more cost and complicated user experience.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
\caption{ Submarine Send~\cite{libsubmarine}. User generates an \textit{Unlock} transaction from which the commitment address is retrieved. By funding the \textit{commitment address}, user is committed to the unlock transaction. After the commitment transaction, in the reveal phase, user sends the \textit{reveal transaction} to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address. Finally after the "Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.  \label{fig:LibSubmarine}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3a259b74-1162-4fb5-8023-eb0311018295

\subsubsection{Design Decision \#3: Logic Specific Solutions\newline}
To prevent front-running, one can design the application in a way that it is not possible to be front-run:

\noindent\emph{Eliminating Time-Order Dependency:} The applications can be designed to not rely on the time for the orders to be executed. For example when designing a decentral exchange, one can use \emph{the call market design} instead of a time-sensitive order book. In a call market design, the arrival time of the orders do not matter as they are executed in batches [cite Jeremy's prediction markets paper].

\noindent\emph{Disincentivizing Front-running Actors:} This solution, which is economic rather than technical, is to disincentives the miners by paying them. As mentioned, the main reasons for miners to front-run the other orders is the financial gain they receive on the price improvement. However, if the application is designed in a way that the fees of the orders are sent to the miner of the block, he would have no incentive to front-run the orders as he already gains enough financial benefit from acting fairly and executing the transactions on their correct order. For example, Malinova~\cite{malinova2017market} proposes a design for a decentral exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.

>>>>

In the traditional markets, front-running is considered unethical and illegal. In the blockchain space, the designers of the decentral applications cannot rely on the justice system for preventing unethical behavior, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain order books. The methods discussed within these projects prevent blockchain network participants from front-running the orders as the orders are private and not known to the network and will not be broadcasted. However they are introducing third parties, \eg relayers in 0xproject, to be managing the orders with the promise not to reorder or front-run other orders.

\emph{Traditional Front-running Prevention Methods}. There are debates in traditional markets regarding the fact that front-running is considered to be a form of insider trading which deemed to be illegal. Traditional methods to prevent front-running mainly involves after the fact investigation and legal action against the front-runners~\cite{LexisNexisLawSuit}. As mentioned in section~\ref{traditionalFrontrunning}, defining front-running and educating the employees were the first step taken to prevent such issues in traditional markets, however front-running became less likely to happen mainly because of the high fine and law suits against firms whom behaved in an unethical way. Other methods such as dark pools~\cite{zhu2014dark, buti2011diving} and sealed bids~\cite{radner1989sealed} were discussed and implemented in variety of regulated trading systems.

@@

There are two main approaches to prevent front-running blockchains: one to design a blockchain that is front-run resistant, and the other to design the application logics in a way that front-running is not possible. 
%______________________________________________________________%
\subsection{Front-run Resistant Blockchain}
There are technical difficulties to achieve such solutions as there are unknown factors within such network designs and requires testing every corner and edge case scenarios. In this section, we describe the potential solutions using which, one can design and implement a decentral application that is resistant to front-running.

\subsubsection{Design Decision \#1: Fixed Transaction Ordering\newline}
One possible solution to fix current blockchains in regards to transaction reordering by miners has been proposed by da Silva~\etal~\cite{fixedordering2018silva}. This solution consists of an algorithm, known as Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions in the mined blocks.

\subsubsection{Design Decision \#2:Privacy Preserving Blockchain\newline}
Market participants are concerned about revealing information on their past trades, purchases, income, or liquidity needs. Privacy is a basic human right, that being said, there are limitations with the functionality of a system designed to preserve full privacy. However other than past transactions, real time transactions would leak informations about the sender or the intention of the order that could lead to front-running attacks. Privacy preserving blockchains try to solve the initial issue by keeping all the details of the transactions private (in some extent~\cite{miller2017empirical, kappos2018empirical}). 
As an example, ZCash~\cite{hopwood2016zcash}, uses two distinct type of addresses, transparent addresses and shielded addresses. Transparent addresses work similar to Bitcoin transactions, fully transparent about the sender and receiver addresses, the amount and included data. However shielded addresses are private and do not leak any information, this is great for privacy but not good for smart contracts capabilities. Smart contract functionality requires verification by the miners which require to know the input, functionality and output of smart contracts to be able to determine if the transaction is valid. Albeit by using cryptographic primitives such as zero-knowledge proofs this issue could also be resolved~\cite{kosba2016hawk}.

\subsubsection{Design Decision \#3: Dual Authoring\newline} % S 2 M: this is still vague, it requires better explanation.
Loopring is an open protocol proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}. This protocol operates a hybrid model with off-chain order management and communication and merely the order matching takes place on the chain. To achieve high liquidity and price improvement, Loopring orders are grouped in \emph{ring orders}. After the required signatures are provided by a miner and owner of the order, see Figure~\ref{fig:vulnerable_loopring}, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement. While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address and then sign the hash of the ring using his own private key. By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}. However, in the new version of Loopring protocol this issue is resolves using the \emph{dual-authoring} scheme. This solution sets two levels of authorization for orders - one for settlement, and one for order matching. As it can be seen in Figure~\ref{fig:not_vulnerable_loopring}, each owner of any order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key. These auth-keys are used to sign the hash of the ring and will further prevent anyone from regenerating the same \emph{submitRing transaction}. The reason is that the auth-keys are only known to the miner of the ring as they are not part of the on-chain transaction. Doing so, it is assured that (i) the orders are not modified (because they are signed by the owner), (ii) no other miner can mine the ring (because the miner's address is signed by the initial miner), and no user can front-run the \emph{submitRing transaction} (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).

% S 2 M: Also I'm not sure about the figures. they do not add enough clarity to the text.

@@

Another method to prevent front-running activities is to design the applications in such a way that there is no information leakage to the malicious parties to enable them to front-run  other users.
Followings discuss a few techniques which can be used by the DApp developers while designing the systems to mitigate front-running issues.

\subsubsection{Design Decision \#1: Commitment Scheme\newline} \label{CommitmentScheme}
Commitment scheme is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}. Commitment scheme is a robust method to prevent information leakage from the sensitive transactions. This could be done by simply submiting the hash value of the committed data to a smart contract and later on revealing the values linked to the committed hash, see Figure~\ref{fig:commitReveal}. 
In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order. This method is not perfect, depending on the DApp design, either the order is collateralized, that means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be vulnerable to Denial-of-Service attacks. 
Another use of such commitment scheme, is in decentralized naming systems, such as Namecoin, Ethereum Name Service (ENS). In this case, a user sends a commit transaction, which commits to the name hash, similar to a sealed bid. Once the transaction is confirmed and the grace period is over, user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}. Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running. Similar approach applies to on-chain voting as well ~\cite{adChainPLCRVoting}, using sealed votes, voters can make sure their votes are hidden until a later date, however their participation and weight of the vote are publicly known. 
Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor. For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, It will be obvious that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme. Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design. On the other note, these method has some drawbacks, the user experience is not smooth and one might forget to reveal the committed transaction. In ENS commit-reveal process, if one forgets to reveal in the reveal phase, the committed funds are burnt and inaccessible there after. Also this scheme means two transaction are required for a functionality which is makes it more expensive to run.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\linewidth]{figures/commit-reveal.png}
\caption{Commit and Reveal. User sends a commitment transaction with the hash of the data, After the commitment period is over, user sends her reveal transaction to the DApp revealing the information that matches the commitment. \label{fig:commitReveal}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3cd4c865-83d4-4c71-9a4a-f2e870f2db2c

\subsubsection{Design Decision \#2: Submarine Commitments\newline}\label{submarineCommits}
Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} are similar to the commitment schemes with some key differences such as hiding participatory factor and being fully collateralized. With submarine send, it is possible to hide sender, receiver, value and data, the commitment transaction is identical to a transaction to a newly generated address. Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants.

The details of how Submarine commitments work is outside the scope of this paper, however in short, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address of which no private key exists. By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}. However, this could be design in other ways to suit the need of the DApp. Drawbacks of this scheme are similar to ~\ref{CommitmentScheme}, with an addition of two more transactions to finalize the functionality, which results in more cost and complicated user experience.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
\caption{Submarine Send~\cite{libsubmarine}. User generates an \textit{Unlock} transaction from which the commitment address is retrieved. By funding the \textit{commitment address}, user is committed to the unlock transaction. After the commitment transaction, in the reveal phase, user sends the \textit{reveal transaction} to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address. Finally after the "Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.  \label{fig:LibSubmarine}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3a259b74-1162-4fb5-8023-eb0311018295

\subsubsection{Design Decision \#3: Logic Specific Solutions\newline}
There is no perfect generic solution to this issue as of now, however to prevent front-running, one can design the application in a way that it is not possible to be front-run:

\noindent\emph{Eliminating Time-Order Dependency:} The applications can be designed not to rely on the time for the orders to be executed. For example when designing a decentral exchange, one can use \emph{the call market} design instead of a time-sensitive order book. In a call market design, the arrival time of the orders do not matter as they are executed in batches~\cite{clark2014decentralizing}.

\noindent\emph{Disincentivizing Front-running Actors:} This solution, which is economic rather than technical, is to disincentives the miners by paying them the fees. If the application is designed in a way that the fees of the orders are sent to the miner of the block, he would have less incentive to front-run the orders as he already gains enough financial benefit from acting fairly and executing the transactions on their correct order. For example, Malinova~\cite{malinova2017market} proposes a design for a decentral exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.
